A template for the \emph{arxiv} style

### 2022-09-20 paper-rmd/paper-papaja-revision.Rmd
submitted

keywords          : "probability judgments, Bayesian cognitive science, heuristics and biases"
wordcount         : "9202"

@@

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
biblio-style      : "apa"
documentclass     : "apa6"
classoption       : "man"
output:
  papaja::apa6_pdf:
    citation_package: biblatex

@@

```{r, fig.cap="Average model predicted and observed values for the 18 identities. Note that the Bayesian Sampler but not the PT+N model is capable of predicting non-zero values for identities Z10 through Z13. In Experiment 1, like participants' responses, the model's estimates are very slightly positive for \\{icy, frosty\\} and very slightly negative for \\{normal, typical\\}. This pattern replicates the qualitative pattern reported by Zhu and colleagues."}
plt_ineq_exp1 + labs(title="Exp. 1") + 
  plt_ineq_exp2 + labs(title="Exp. 2") + 
  plot_layout(guides="collect") & theme(legend.position="bottom") & labs(color="", y = "Estimate", x = "Identity")
```

@@

```{r, fig.cap='Posterior predictions for best-fitting model and participants responses in Experiments 1 and 2.'}
plt_pp
```

@@

First, it is clear that participants have rounded a majority of their responses. This sort of rounding can be modeled by a categorical distribution across the discrete possible rounded responses. Each rounded response category corresponds to a set of cut points, $a$ and $b$, with the probability of the categorical response defined by the CDF of the Beta distribution.

@@

Where $B$ is the cumulative distribution function of the underlying latent distribution. As participants were allowed to respond freely with whole numbers from 0 to 100, the exact rounding policy for each response is unknown. Nevertheless these rounding policies can be estimated via mixture modeling. For simplicity, rounding to the nearest 5% was enforced for all responses. Then, the probability of these categorical responses are computed for 21 and 11 categories (corresponding to rounding to 5% and 10%). These probabilities were combined along with a uniform probability representing "contaminants" according to mixing probabilities $\phi$, distributed with a Dirichlet prior (see Appendix for further implemenatation details).

@@

Nevertheless we might still use the logic of Bayesian models to understand the operation of these beliefs and how they respond to evidence. Indeed, by representing the "true" subjective probabilities as a latent variable in the models used here, Bayesian data analysis allows those underlying credences to be inferred. Future research could explore how estimates of people's credences might be made more reliable, and how inferences about these mental probabilities might be integrated with other Bayesian models of reasoning [e.g. @franke.etal2016; @jern.etal2014; @griffiths.tenenbaum2006]. For instance, people's responses in various reasoning tasks are often explicitly related to inferred subjective mental probabilities, so accounting for biases in those reports may permit more rigorous model testing. One particularly promising direction could be to integrate these models with formal models of belief revision, which might then shed new light on these fundamental cognitive processes [e.g. @edwards1968; @cook.lewandowsky2016; @jern.etal2014; @powell.etal2018; @powell2022].
\pagebreak

@@

Where $B$ is the appropriate cumulative distribution function. To capture rounding to 10 we define $a_{i,10} =  \frac{2i}{m}-\frac{1}{m}$ and $b_i = \frac{2i}{m}+\frac{1}{m}$, so that the probability of each response is:

>>>>

keywords          : "probability judgments, Bayesian cognitive science, heuristics and biases"
wordcount         : "9374"

@@

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
biblio-style      : "apa"
documentclass     : "apa6"
classoption       : "man"
output:
  papaja::apa6_pdf

@@

```{r, fig.cap="Average model predicted and observed values for the 18 identities. Note that the Bayesian Sampler but not the PT+N model is capable of predicting non-zero values for identities Z10 through Z13. Error bars represent 95% CI. In Experiment 1, like participants' responses, the model's estimates are very slightly positive for \\{icy, frosty\\} and very slightly negative for \\{normal, typical\\}. This pattern replicates the qualitative pattern reported by Zhu and colleagues."}
plt_ineq_exp1 + labs(title="Exp. 1") + 
  plt_ineq_exp2 + labs(title="Exp. 2") + 
  plot_layout(guides="collect") & theme(legend.position="bottom") & labs(color="", y = "Estimate", x = "Identity")
```

@@

```{r, fig.width=6, fig.height=3, fig.cap='Posterior predictions for best-fitting model and participants responses in Experiments 1 and 2.'}
plt_pp
```

@@

First, it is clear that participants have rounded a majority of their responses. This sort of rounding can be modeled by a categorical distribution across the discrete possible rounded responses. Each rounded response category corresponds to a set of cut points, $a$ and $b$, with the probability of the categorical response defined by the cumulative distribution function of the underlying latent distribution.

@@

As participants were allowed to respond freely with whole numbers from 0 to 100, the exact rounding policy for each response is unknown. Nevertheless these rounding policies can be estimated via mixture modeling. For simplicity, rounding to the nearest 5% was enforced for all responses. Then, the probability of these categorical responses are computed for 21 and 11 categories (corresponding to rounding to 5% and 10%). These probabilities were combined along with a uniform probability representing "contaminants" according to mixing probabilities $\phi$, distributed with a Dirichlet prior (see Appendix for further implemenatation details).

@@

Nevertheless we might still use the logic of Bayesian models to understand the operation of these beliefs and how they respond to evidence. Indeed, by representing the "true" subjective probabilities as a latent variable in the models used here, Bayesian data analysis allows those underlying credences to be inferred. Future research could explore how estimates of people's credences might be made more reliable, and how inferences about these mental probabilities might be integrated with other Bayesian models of reasoning [e.g. @franke.etal2016; @jern.etal2014; @griffiths.tenenbaum2006]. For instance, people's responses in various reasoning tasks are often explicitly related to inferred subjective mental probabilities, so accounting for biases in those reports may permit more rigorous model testing. One particularly promising direction could be to integrate these models with formal models of belief revision, which might then shed new light on these fundamental cognitive processes [e.g.  @cook.lewandowsky2016; @jern.etal2014; @powell.etal2018; @powell2022].
\pagebreak

@@

where $B$ is the appropriate cumulative distribution function. To capture rounding to 10 we define $a_{i,10} =  \frac{2i}{m}-\frac{1}{m}$ and $b_i = \frac{2i}{m}+\frac{1}{m}$, so that the probability of each response is:
